\section{Limitations}\label{sec:limitations}

% Limitations. What should be left out and why?

Due to time constraints and the scope of this thesis, there will be several limitations to the work presented:
\begin{itemize}
    \item The work will be limited to only testing a single head / type of loss for the neural compression model. While it would be interesting to explore multiple heads, this would be time consuming in testing when running all the model variations. 
    \item The work will only implement the encoder and tokenizer part of the pipeline while forgoing the entropy coding. This is done due to the focus of the thesis being on the neural compression step and while entropy coding is important in a full compression pipeline, it is less relevant for the research question at hand. 
    \item The work will also forgo testing on real hardware as that would be very time consuming and difficult to set up while contributing relatively little to the main research question.
    \item The work will be limited to only testing regression tasks and anomaly detection as downstream tasks due to time constraints and structure of the available datasets. These two tasks should however be a good representation of common downstream tasks and adding more tasks would likely not drastically change the conclusion of the thesis. 
    \item Due to wanting to keep the compressed data representation as versatile as possible, no task-aware compression techniques will be implemented. While task-aware compression could potentially yield better performance for specific tasks, it would limit the generalizability of the compressed representation and add significant complexity to the work. It also results in a more relevant comparison to other compression techniques which are not task-aware. 
\end{itemize}