\section{Timeline}\label{sec:timeline}

We want to roughly divide the project into four stages, each with specific goals and deadlines. First, we will set up a working environment, and put time into understanding the problem and plan for the project. This would be \textbf{Stage 1: Setup and Preparation}. Within this stage we have the following sub-goals: 
\begin{itemize}
    \item Planning the project with appropriate subtasks and a timeline. Then writing the project plan.
    \item Creating a working environment. This include setting up necessary hardware (at Volvo), git repositories, and coding environments. 
    \item Defining and Training a downstream ML model on uncompressed data that will serve as a benchmark for evaluating the performance of different compression methods. Right now, we aim for one regression and one classification task based on automotive telemetry data. 
    \item Implementing a baseline model based on an established neural compression frameworks such as \url{https://www.sciencedirect.com/science/article/pii/S1568494623008153}. The planned architecture is discussed in section~\ref{sec:methodology}.
\end{itemize}

We envision, that this stage will take roughly five weeks and set a preliminary deadline for the 20th of February.

The second stage, \textbf{Stage 2: Development}, will focus on developing the core components of the proposed compression approach leveraging tokenization. This includes:

\begin{itemize}
    \item Develop a compression framework that leverages tokenization. This includes implementing an encoder, a quantization method using a codebook, and a decoder as discussed in section~\ref{sec:methodology}.
    \item Conducting some first initial experiments to validate the implementation. 
    \item Writing the halftime report. 
    \item Start writing on the final thesis report. At this stage we aim to have the theory part of the report done.
\end{itemize}

The second stage should take around five weeks as well, with a deadline for the 27th of March.

After that, we will start \textbf{Stage 3: Experiments}, which will focus on evaluating the performance of the proposed compression method against the baseline model. This stage will include:

\begin{itemize}
    \item Compressing the data using both the baseline compression method and the proposed tokenization approach.
    \item Training the downstream model on the compressed data using both compression methods.
    \item Evaluating the experiments by capturing the defined metrics for both compression methods. 
\end{itemize}

This stage is expected to take three weeks, with a deadline for the 17th of April.

Finally, we will enter \textbf{Stage 4: Finalizing}, which will involve:

\begin{itemize}
    \item Conducting an ablation study of the proposed tokenization compression framework.
    \item Writing the methodology, results, discussion, and conclusion part for the final report.
\end{itemize}

This stage is expected to take four weeks. We plan to have a first draft of the final report ready with a deadline for the 15th of May.